```{r}
library(tidyverse) #tidyverse set of packages and functions
library(tidymodels)
library(glmnet) #for Lasso, ridge, and elastic net models 
library(GGally) #create ggcorr and ggpairs plots
library(ggcorrplot) #create an alternative to ggcorr plots
library(MASS) #access to forward and backward selection algorithms
library(leaps) #best subset selection
library(lmtest) #for the dw test
library(splines) #for nonlinear fitting
library(lubridate)
```
 
```{r}
bike = read.csv('bike_cleaned-3.csv')
```
```{r}
bike = bike %>%mutate(dteday = mdy(dteday))
```

```{r}
bike = bike %>% mutate_if(is.character, as_factor)
```


```{r}
bike = bike %>% mutate(hr = as_factor(hr))
```

```{r}
ggcorr(bike, label = "TRUE", label_round = 1)
ggpairs(bike, columns = c("count", "windspeed", "hum","atemp","temp"))
```

Question 1 Which of the quantitative variables appears to be best correlated with “count”? NOTE: Ignore
the “registered” and “casual” variable as the sum of these two variables equals “count”. Because these
variables combine to make the response variable, they cannot be used as predictors. You can also ignore the
“instant” variable as it is just a row number. A. Temp

```{r}
ggplot(bike, aes(x = season, y = count)) + geom_col()
```
Question 2 Which “season” appears to have the highest count of rides? C. Summer

```{r}
bike_recipe = recipe(count ~ hr, bike) %>%
  step_dummy(hr)

lm_model = #give the model type a name 
  linear_reg() %>% #specify that we are doing linear regression
  set_engine("lm") #specify the specify type of linear tool we want to use 

lm_wflow = 
  workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(bike_recipe)

lm_fit = fit(lm_wflow, bike)
```


```{r}
summary(lm_fit$fit$fit$fit)
```
Question 3 Build a linear regression model (using tidymodels) with “hr” to predict “count”. You will use
this model to answer the next several questions.
How many dummy (indicator) variables are used to represent “hr” in the model? 24

Question 4 In your model from Question 3, which hour is selected as the “base” level (category)? The base
level does not have an associated coefficient (slope) in the linear regression model. 0

```{r}
ggplot(bike, aes(hr, count)) + geom_point()
```
```{r}
Predictor = lm_fit%>%
  extract_fit_parsnip() %>%
  tidy()
```

Question 5 During which hour of the day does the model predict the highest number of rides? 17

```{r}
ggplot(bike, aes(temp, count)) + geom_point()
```
Question 6 Plot “temp” (x axis) versus “count” (y axis) using an appropriate plot type.
Which statement best describes the general relationship between “temp” and “count”? A

```{r}
bike_recipe2 = recipe(count ~ hr + temp, bike)
 

lm_model = #give the model type a name 
  linear_reg() %>% #specify that we are doing linear regression
  set_engine("lm") #specify the specify type of linear tool we want to use 

lm_wflow2 = 
  workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(bike_recipe2)

lm_fit2 = fit(lm_wflow2, bike)

summary(lm_fit2$fit$fit$fit)
```
Question 7 Create a linear regression model (using tidymodels) with “hr” and “temp” to predict “count”.
You will use this model to answer the next several questions.
What is the value of the slope coefficient for “hr23” in this model (to three decimal places)? 31.748 

Q8. Adjusted R-squared:  0.5886 

```{r}
bike_recipe3 = recipe(count ~ atemp + temp, bike)
 

lm_model = #give the model type a name 
  linear_reg() %>% #specify that we are doing linear regression
  set_engine("lm") #specify the specify type of linear tool we want to use 

lm_wflow3 = 
  workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(bike_recipe3)

lm_fit3 = fit(lm_wflow3, bike)

summary(lm_fit3$fit$fit$fit)
```

Q9. Adjusted R-squared:  0.1638 

Q10. TEMP Only

Q11. D

```{r}
allmod = lm(count ~ season + mnth + hr + holiday + weekday + workingday + weathersit + temp + atemp + hum + windspeed, bike) #use the ~. to include all predictors rather than typing them all in
summary(allmod)

```

```{r}
backmod = stepAIC(allmod, direction = "backward", trace = TRUE)
summary(backmod)
```

q12. B. Weekday + holiday

q13. B. WorkingDay
